\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage{biblatex}
\usepackage{import}
\usepackage[acronym]{glossaries}
\usepackage{todonotes}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{tikzit}

\import{./src/figures/}{test_style.tikzstyles}

\addbibresource{./src/bibliography.bib}

\import{./src/}{glossary.tex}

\title{Adapt the \acrlong{nrpa} to solve stochastic problem}
\author{Thomas Petiteau}
\date{november 20 2020}

\begin{document}
    \maketitle
    \clearpage

    \tableofcontents
    \clearpage

    \section{Introduction}%
    \label{sec:introduction}
    
    The \gls{mcts} is a family of algorithm that have successfully applied to a lot of problems and games \cite{survey_mcts}.
    In particular, the \gls{nrpa} has been recently used to solve optimization problem such as \gls{tsptwm}\cite{nrpa_tsptw} and it obtains state of the art result on many.
    It has found new records in Morpion Solitaire and crosswords puzzle.
    But it only performs well on non stochastic problem which compose a small portion of more practical importance.
    In this paper, we present an adaptation of the \gls{nrpa} to stochastic context resulting in a new algorithm we call \gls{snrpa}.
    We will first present the \gls{mcts} and then the \gls{nrpa}. We will then proceed to explain the difficulty of solving stochastic problems with the \gls{nrpa}.
    Finally, we will introduce the new \gls{snrpa} and we will try it on instances of the \gls{twm} problem with other algorithms to compare their performance.
    

    \import{./src/sections/mcts/}{mcts.tex}
    \clearpage
    \glsresetall{}
    \import{./src/sections/nrpa/}{nrpa.tex}
    \clearpage
    \glsresetall{}
    \import{./src/sections/snrpa/}{snrpa.tex}
    \clearpage
    \glsresetall{}
    \import{./src/sections/twm/}{twm.tex}
    \clearpage
    \glsresetall{}
    \import{./src/sections/experiments/}{experiments.tex}
    \clearpage

    \section{Conclusion}%
    \label{sec:conclusion}
    
    In this paper, we presented the \gls{nrpa}, a \gls{mcts} algorithm, giving state of the art results on many optimization problem.
    We presented the \gls{snrpa}, an adaptation of the \gls{nrpa} to solve stochastic problem.
    Our results show that the \gls{snrpa} performs very well on the \gls{twm} problem.
    Future works include the test on other stochastic problems and on non stochastic problems to compare the \gls{snrpa} to the \gls{nrpa} on territory dominated by the \gls{nrpa}.
    We would also want to present more computational demanding results to see if the gap of performance between the algorithms is more significant.

    \printbibliography{}
\end{document}

